\chapter{Command Line Tool}
In this chapter we describe \texttt{msp} --- a command line tool we created
to facilitate usage of the MySQL Operator. First, we explain the basic
\textbf{CLI}~\footnote{Command-Line Interface} concept, followed by a description
of technologies used, and finally a detailed description of the functionalities
provided by our tool. We also provide a few usage examples to outline the most
common use cases.

\section{CLI Basics}
\texttt{msp} provides a layer of abstraction over management of MySQLCluster
and MySQLBackupSchedule objects. Rather than writing verbose yaml files and manually
modifying Kubernetes’ configuration via \texttt{kubectl}, a user can easily
perform most actions related to managing their MySQL cluster with a single
\texttt{msp} command. Additionally, a CLI tool like this helps inexperienced users
get started with our system, and allows Kubernetes system administrators to
write more concise and expressive automation scripts.

\section{Technologies}
Like the rest of our project, \texttt{msp} is written in Go. Our implementation
bases on Cobra~\cite{cobra} --- a~framework for writing command line interfaces
similar to many UNIX shell programs. Cobra is widely used in the Go and
Kubernetes ecosystems, most prominently in \texttt{kubectl} itself. The~ library
is designed to facilitate the creation of easily extensible and
customizable CLI tools. Cobra programs are typically called with a list
of structured arguments specifying an object, an action to perform on the
selected object, and optionally a list of flags that customize the program’s
behavior.

\section{Functionalities}
The treelike command structure implies the natural order of the whole CLI
tool. Consequently, each command in our tool has the following form:

\vspace{.75em}
\centerline{\texttt{msp \textit{resource-type action resource-name flags}}}
\vspace{.75em}

\texttt{msp} can be used to create, update, or delete both MySQLClusters
and MySQLBackupSchedules. Flags can be global or local, referring
to resource types and actions. To set global options, needed for proper
functioning of the program, \texttt{msp} uses the following flags:
\begin{itemize}
    \item \texttt{kubeconfig} --- location of the kubeconfig file needed to
        establish a network connection with a Kubernetes cluster.
    \item \texttt{namespace} --- Kubernetes namespace in which resources will be created.
    \item \texttt{force} --- to ignore errors during cascade deleting.
\end{itemize}


\section{MySQL Operator Use-cases}

These use cases show most of the actions that can be performed to manage a cluster and its data.

\subsection{Cluster}

\subsubsection*{Create}
\noindent Creating a new cluster with an already exisiting Secret.

\begin{lstlisting}
> msp cluster create "my-cluster" --secret "my-secret"
\end{lstlisting}

\noindent Creating a new cluster along with defining a new Secret.

\begin{lstlisting}
> msp cluster create "my-cluster" --secret "my-secret" \
	--password "password"
\end{lstlisting}

\noindent Creating a new cluster from a backup instance.

\begin{lstlisting}
> msp cluster create "my-cluster" --backup "backup-name" \
	--instance "backup-instance"
\end{lstlisting}

\noindent Creating a new cluster with a specified port, image, storage, and number of replicas.

\begin{lstlisting}
> msp cluster create "my-cluster" --port 1337 --image mysql:img \
	--replicas 7 --secret "my-own-secret"
\end{lstlisting}

\subsubsection*{Delete}

\texttt{msp} provides users with more functionalities. Users can perform a hard
delete, removing not only the cluster but also all database information.

\noindent Deleting two clusters.

\begin{lstlisting}
> msp delete cluster "my-cluster" "my-cluster2"
\end{lstlisting}

\noindent Deleting a cluster along with PVC’s.

\begin{lstlisting}
> msp delete cluster "my-cluster" --remove-pvc
\end{lstlisting}

\subsubsection*{Update}
\noindent Updating a cluster with a new Secret, port, and number of replicas.

\begin{lstlisting}
> msp update cluster "my-cluster" --replicas 4 --port 1337 \
	--secret "my-new-secret"
\end{lstlisting}

\subsection{Backup}

\subsubsection*{Create}
\noindent Creating a backup schedule that creates a backup instance at 23:59 December 31 every year.

\begin{lstlisting}
> msp create backup --cluster "my-cluster" \
	--time "59 23 31 DEC Fri *"
\end{lstlisting}

\noindent Creating a backup schedule named "elite" in Kubernetes that creates
a backup instance at 13:37 every day. The 2Gi of storage is shared among
the backup instances.

\begin{lstlisting}
> msp create backup --name "elite" --cluster "my-cluster" \
	--time "13 37  *  *  * *" --storage 2Gi
\end{lstlisting}

\subsubsection*{Delete}
\noindent Deleting two backup schedules.

\begin{lstlisting}
> msp delete backup "my-backup" "my-backup2"
\end{lstlisting}

\noindent Deleting a backup schedule along with its PVC's.

\begin{lstlisting}
> msp delete backup "my-backup" --remove-pvc
\end{lstlisting}

\subsubsection*{Update}
\noindent Updating a backup schedule's time field.

\begin{lstlisting}
> msp update backup "my-backup" --time "12 20 * * * *"
\end{lstlisting}
