\chapter{Development Stack}
\section{Version Control System}
Our VCS of choice is \textbf{Git}, and our repositories are hosted on \textbf{GitHub}. Being the most popular service,
GitHub is well integrated with many developer tools such as Golang’s \texttt{go get} and various Continuous Integration systems.
On top of that, we use common GitHub features for managing current tasks and project development.
\subsection{Workflow}
We follow a fairly standard git workflow. New features are developed on separate branches, branched directly off of \texttt{master}.
Once the code is ready, the branch is pushed to our central GitHub repository and code review is requested from other team members.
After positive feedback from the CI system and two approvals, the pull request is merged to the \texttt{master} branch.
To retain a linear git history, all feature branches are rebased onto the \texttt{master} branch before merging.
\section{Continuous integration}
\subsection{Jenkins}
Due to our familiarity with \textbf{Jenkins}~\cite{jenkins}, it was our first choice when approaching \textit{continuous integration}. Jenkins was
deployed on a low---spec VPS (\textit{OpenVZ} virtualization). This system was sufficient for the simplest use case --- Golang unit
testing and notifications through Slack. However, the outdated Linux kernel (2.6.32) on the host machine was not compatible with 
Docker\footnote{Docker requires version 3.10 or higher} (crucial for Kubernetes), which (along with the necessity to maintain the server ourselves)
convinced us to look for an alternative.
\subsection{Travis}
\textbf{Travis CI}~\cite{travis} is a hosted service (free for open source projects). Unlike Jenkins, it does not require server---side configuration,
but relies only on \texttt{.travis.yml} files placed inside the project source directory (similar functionality in Jenkins can be achieved by using
the Pipeline plugin~\cite{jnk-pipeline}). This makes it easy to have different test code per branch and removes the necessity to manage permissions
separately for the repository and for the CI system. Travis integrates easily with the tools used in our project (GitHub and Slack). Along with
Travis CI, we have decided to use \textbf{Coveralls}~\cite{coveralls} --- a web service that tracks code coverage\footnote{the degree to which the
source code of a program is executed when a particular test suite runs} over time, and ensures that all new code is fully covered by tests.
\subsection{Kubernetes Cluster}
To perform integration tests during the continuous integration process we have decided to use \textbf{Minikube}~\cite{minikube} --- a lightweight
Kubernetes implementation that creates a VM on the local machine and deploys a simple cluster containing only one node.
\subsection{Continuous Deployment}
The Docker image built from the \texttt{master} branch is automatically deployed to \textbf{DockerHub}~\cite{docker}. This way users can download
and use our project easily as a docker image. Each stable version of our project is manually added and reflects a specific git commit.
\section{Communication}
As our communication tool, we have chosen \textbf{Slack}~\cite{slack} --- a modern IRC---like communicator. Slack features persistent chat rooms
(channels) organized by topic, comes with a large number of third---party services, and supports community---built integrations.