\chapter{Introduction}
In the fast-paced world of modern web technologies, services are expected to
efficiently and reliably process large amounts of data. As such, developers
and system administrators want to create systems that are scalable. Scalability,
while desirable, is an issue that significantly adds to the complexity of
problems faced by software engineers every day. This has led to the emergence of
technologies that orchestrate entire clusters, providing automatization that
makes managing such systems easier.

\textit{Kubernetes} is an open-source container orchestrator developed by
Google. It is used by leading tech companies to automate the deployment,
scaling, and management of their applications~\cite{kube-usecase}. Its common
use cases are cloud computing systems and microservices-oriented architectures.

The main feature provided by \textit{Kubernetes} and similar orchestration
systems is the management of containerized applications. Containers are
a~lightweight and portable alternative to virtual machines. In recent years,
the~advantages of containerization have been recognised, which has led to
the~rapid development of supporting technologies, such as Docker or rkt.

A central part of many web applications is a~performant database. Despite
the~variety of new database engines constantly appearing on the market, many
developers still decide to rely on \textit{MySQL}. According to the db-engines
statistics~\cite{db-eng}, \textit{MySQL} is the second most used database
engine.

Our project is focused on developing tools for creating and managing
a~\textbf{LAMP}\footnote{Linux host with Apache web server, MySQL database
and PHP programming language} stack in \textit{Kubernetes}. Our main goal is to
extend the \textit{Kubernetes API} with options for \textit{MySQL} database
management and provide users with a user-friendly command line tool. As
a~result, developers should be able to more effortlessly benefit from
\textit{Kubernetes’} advantages, such as scalability. Leveraging the powerful
abstraction system provided by \textit{Kubernetes} in such a way will remove
much of the complexity traditionally caused by the database layer of
an~application.

There are existing unofficial tools with similar functionalities for various
databases and systems. \textit{Vitess}~\cite{vitess} is an~open source
clustering system for \textit{MySQL} databases that can interface with
\textit{Kubernetes}. We are aiming for a simpler solution that utilizes
\textit{Kubernetes'} native method of extending its API ---
\textbf{Custom Resource Definitions} (CRDs). Another existing tool,
\textit{Postgres operator}~\cite{psql-op}, is closer in scope to what we want to
accomplish, providing a CustomResourceDefinition for \textit{Postgres} 
databases instead of \textit{MySQL}.

This dissertation is divided into eight chapters. We start with the necessary 
preliminary knowledge about Kubernetes and Custom Resources. Next, we cover 
our workflow and development stack. The main chapter describes the design and 
implementation details of the MySQL Operator functionalities. The following 
chapter consists of essential information of the command line interface we 
provided to facilitate the usage of our tools. The final sections explain main 
design decisions, obstacles encountered, and future considerations for further 
work on the project.

We were working together on all parts of the implementation, however there are 
some areas which certain team members were responsible for. Marcin Chrzanowski 
was involved in Stateful Set and MySQL Cluster creation and deletion. Jakub 
Sarzyński’s main task was to provide a Command Line Interface for our tools. 
Agnieszka Świetlik was responsible for backups design and implementation. Mikołaj 
Walczak was the core of our team, he was in charge of Continuous Integration, 
testing and putting the project parts together. Disregarding this basic division, 
we worked as a team and every member participated equally in the creation process 
of this project and dissertation.
